### 2011-02-10 paper/results.tex
5.3

The results for the gaits produced and evolved by HyperNEAT are shown
in \figref{hnResults} and \tabref{results}.  Overall the evolved gaits
were the fastest by far, beating all the parameterized models when
comparing either the average or the best gaits of each.

>>>>

The results for the gaits produced and evolved by HyperNEAT are shown
in \figref{hnResults} and \tabref{results}.  Overall the evolved gaits
were the fastest by far, beating all the parameterized models when
comparing either the average or the best gaits of each.  We suspect
that this is due to the fact that HyperNEAT was allowed to explore a
much richer space of motions, but did so while still utilizing
symmetries when advantageous.
\figref{neat_110115_211410_00000_002_filt_zoom} shows a typical
HyperNEAT gait that had high fitness.  The pattern of motion is both
complex --- containing multiple frequencies and repeating patterns ---
and reuses patterns for multiple motors.
